### 2020-06-30 2020/wada/adaptive_domain_adaptation.tex
correct some errors

We define some important constants:
\begin{itemize}
\item Inseparability of domains over a given fixed representation space $\Omega$
\begin{equation}
  \begin{split}
  \mathbb{\varepsilon}_{insep} = \min_{p} \sum_{k\in[1..K]} \mathbb{E}_{x,y \sim \sum_{i\in [1..K]} \mathcal{D}_{i}*p(d=i)}(\mathbf{1}_{d\neq k} p(k|h))
  \end{split}
  \end{equation}
\item Inseparability of domain k from other domains over a given fixed representation space $\Omega$
  \begin{equation}
  \begin{split}
  \mathbb{\varepsilon}_{insep}^k = \min_{p} \mathbb{E}_{x,y \sim \sum_{i\in [1..K]} \mathcal{D}_{i}*p(d=i)}(\mathbf{1}_{d\neq k} p(k|h))
  \end{split}
  \end{equation}
\item Risk of the generic model: $\mathbb{R} = \mathbb{E}_{(x,y \sim \sum_{k}p(x,y|d=k)p(d=k)) \sim \mathcal{D}}(l(M(x,y_{<t}), y_t))$ \fyTodo{wrt to which distribution ?}
\item $\mathbf{\Omega_{k,p_{0}}} = \lbrace h | z_k = p_\theta(k|h) < p_0\rbrace$.
\item Risk of the adapted model for the in-domain test set:
  $$R_k = \mathbb{E}_{x,y \sim \mathcal{D}_k} [l(h + a_k(h) * f(z_k), y)]$$
\end{itemize}

>>>>

We define some important constants:
\begin{itemize}
\item Inseparability of domains over a fixed representation space $\Omega$
\begin{equation}
  \begin{split}
  \mathbb{\varepsilon}_{insep} = \min_{p} \sum_{k\in[1..K]} \mathbb{E}_{x,y \sim \sum_{i\in [1..K]} \mathcal{D}_{i}*p(d=i)}(\mathbf{1}_{d\neq k} p(k|h))
  \end{split}
  \end{equation}
\item Inseparability of domain k from other domains over a fixed representation space $\Omega$
  \begin{equation}
  \begin{split}
  \mathbb{\varepsilon}_{insep}^k = \min_{p} \mathbb{E}_{x,y \sim \sum_{i\in [1..K]} \mathcal{D}_{i}*p(d=i)}(\mathbf{1}_{d\neq k} p(k|h))
  \end{split}
  \end{equation}
\item Risk of the generic model: $\mathbb{R} = \mathbb{E}_{(x,y \sim \sum_{k}p(x,y|d=k)p(d=k)) \sim \mathcal{D}}(l(M(x,y_{<t}), y_t))$ \fyTodo{wrt to which distribution ?}
\item $\mathbf{\Omega_{k,p_{0}}} = \lbrace h | z_k = p_\theta(k|h) < p_0\rbrace$.
\item Risk of the adapted model for the in-domain test set:
  $$R_k = \mathbb{E}_{x,y \sim \mathcal{D}_k} [l(h + a_k(h) * f(z_k), y)]$$
\end{itemize}
